Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-11 paper/galsize_paper.tex
Updated figures with larger labels
Update text with description of expanded lensing predictions

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction.pdf}
\caption{
{\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, we make predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}. As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be significantly stronger relative to large galaxies of the same stellar mass. To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the trend is reversed and weakened: for both blue and red samples, $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
}
\label{fig:lensingprediction}
\end{figure}
%-----------------------------------------------------------------------------------------------------

@@

The $\rhalf-$dependence of galaxy lensing has recently been measured using CFHTLenS observations \citep{heymans_etal12,erben_etal13}. For both red- and blue-sequence galaxies, it was found in \citet{charlton_etal17} that the lensing signal, $\Delta\Sigma,$ of large galaxies is slightly stronger relative to smaller galaxies. This result is in good agreement with the clustering measurements in the top panels of Figure \ref{fig:colorclustering}, which show the same trend. To date, the $\rhalf-$dependence of $\Delta\Sigma$ not yet been measured for $\mstar-$complete samples. We show  predictions of the $\rvir-$based model for future measurements of this signal in Figure \ref{fig:lensingprediction}. The halo model explanation for this trend is the same as for $\wproj:$ satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples.

>>>>

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction.pdf}
\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm9p75_sm10p25.pdf}
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction2.pdf}
\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm10p25_sm10p75.pdf}
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction3.pdf}
\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm10p75_sm11p25.pdf}
\caption{
{\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, in the {\em left panels} we show predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}. To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the trends shown here are reversed and weakened: for both blue and red samples, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies. As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be significantly stronger relative to large galaxies of the same stellar mass $\mstar\lesssim10^{11}\msun.$ We additionally predict that at sufficiently large mass $\mstar\gtrsim10^{11}\msun,$ the trend of small-scale $\Delta\Sigma$ with $\rhalf$ should reverse sign. The {\em right panels} display the physical explanation for this prediction. For $\mstar\lesssim10^{11}\msun,$ satellites preferentially populating the small sample heavily weight high-mass halos, boosting the lensing signal on all scales. For $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10\%,$ central galaxies dominate the signal, and the $\rvir-$based model predicts that $\rhalf$ increases with $\mhalo$ for centrals. See text for further details. 
}
\label{fig:lensingprediction}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

@@

The $\rhalf-$dependence of galaxy lensing has recently been measured using CFHTLenS observations \citep{heymans_etal12,erben_etal13}. For both red- and blue-sequence galaxies, it was found in \citet{charlton_etal17} that the lensing signal, $\Delta\Sigma,$ of large galaxies is slightly stronger relative to smaller galaxies. This result is in good agreement with the clustering measurements in the top panels of Figure \ref{fig:colorclustering}, which show the same trend.

To date, the $\rhalf-$dependence of $\Delta\Sigma$ not yet been measured for $\mstar-$complete samples. In the left panels of Figure \ref{fig:lensingprediction}, we show predictions of the $\rvir-$based model for future measurements of $\Delta\Sigma.$ The halo model principles underlying the lensing trends are the same as for $\wproj.$ For $\mstar\lesssim10^{11}\msun,$ the difference in $F_{\rm sat}$ between small and large samples is the dominant factor; satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples. At sufficiently large stellar mass $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10\%,$ the role of centrals becomes dominant; the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals, which is reflected in the reversal of the small-scale signal in the bottom left panel.

The right panels of Figure \ref{fig:lensingprediction} compare the distributions of host halo mass for small and large samples; for centrals, $\mhost=\mhalo,$ while for satellites, $\mhost$ is the virial mass of the parent halo. The peak of each distribution arises from central galaxies, while the long tail at large values of $\mhost$ is due to satellites. At all stellar mass, the blue histograms peak at slightly larger $\mhost$ relative the red, because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals. For $\mstar-$complete samples, this effect only becomes dominant when the satellite fraction drops to sufficiently small values. Qualitatively, all of these features are completely generic predictions of the $\rvir-$based model; quantitatively, the precise value of $\mstar$ where the effect of centrals begins to dominate $\Delta\Sigma$ depends sensitively on $F_{\rm sat}(\mstar),$ which we have only roughly calibrated in the present work.
